{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-29 wacv_for_review.tex
Revised for Deep Features

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and executable code. To develop a single,
target tracking system in high accuracy and run-time performance while
these criteria kept in mind, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn. For
a smooth transition between individual KCFs' executions, we developed
a Bayes filter. Experimental results showed that the performance of
ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. These results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Moreover our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps) for UAV123.
\end{abstract}

@@

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence. This is based on an assumption that the scale of a target
would not change much over two consecutive frames. Similarly, Ma and
his colleagues used two KCFs to learn the translation and scale of a
target separately \cite{ma2015long}. In particular, a KCF is used to
learn the translation of the target and its background. Given this,
another KCF is used to learn the target area to estimate a new scale
of the target. However, because of running more than a KCF on each
frame, this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. Figure \ref{Workflows}
illustrates the work-flow of the {\it E}nKCF. In particular, to
maximize run-time performance and accuracy, instead of running them
all together on every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing a scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{fig:Filters} shows
examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$.

\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
In this paper, we propose a novel way of utilizing a multiple of the
KCFs \cite{henriques2015high} to effectively handle scale variations
and dynamic maneuvers of a target. To maintain or improve the run-time
performance of the original KCF (e.g., $\ge$ 300), we deploy three
KCFs in turn, instead of applying them on the same image frame
together. Each of these KCFs is designed to address specific
challenges, i.e., scale and translation. By alternating their
deployments, our algorithm will improve the performance of the
original KCF while preserving the efficient nature and small-footprint
of the KCF computation.

@@

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.

\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 data is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 data, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, we call it
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

\textbf{Features Selections} We used different features for each of
three KCFs as each of them has different goals to accomplish. In
particular, the translation filter, $R_{t}^{L}$, uses both the fast
Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to more effectively
learn the background around the target. Through experiments, we found
that only fHoG didn't work well to cover a larger ROI; another
translation filter, $R_{t}^{S}$, worked well when it used fHoG
features only; the scale filter, $R_{s}$ did when it used both fHoG
and color features.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. We hypothesize that the {\it E}nKCF
tracker could perform better with deep features trained on ImageNet
dataset. Utilizing pretrained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. But as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ CNN features.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

  Burak: We don't expect the reviewers or readers to exactly see what
  we saw here. Keep their scales same -- whatever maximum value you
  choose for the y-axis for one graph, use the same scale to all other
  same graphs.}
\end{comment}
There have been many studies on applying a pretrained CNN features to
tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet
\cite{simonyan2014very} for this idea where their experiments showed
that the first convolutional layer features lead to slightly better
precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
features. Their method employs the third convolutional layer features
to get the response map. In the next stage, they used the estimation
of the target's transition from the first stage to use the second
convolutional layer features. Finally, the first convolutional layer
features is extracted from the position estimated in the second
stage. This coarse-to-fine position estimation approach allows to
utilize more representative features of the object. However, such
approach requires multiple runs of a KCF at a single frame, increasing
the run-time complexity. For this reason, we follow a similar approach
to \cite{danelljan2015convolutional} to embed deep learning features.

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC).

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and executable code. To develop a single,
target tracking system in high accuracy and run-time performance while
these criteria kept in mind, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn and assign 
them hand-crafted features including histogram of oriented gradients and color features.
For a smooth transition between individual KCFs' executions, we developed
a Bayes filter. Experimental results showed that the performance of
ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. These results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Moreover our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps) for UAV123. Finally, for the embedded
systems with GPUs, we explored different levels of deep features for different
correlation filters to boost tracking performance. 
\end{abstract}

@@

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence. This is based on an assumption that the scale of a target
would not change much over two consecutive frames. Similarly, Ma and
his colleagues used two KCFs to learn the translation and scale of a
target separately \cite{ma2015long}. In particular, a KCF is used to
learn the translation of the target and its background. Given this,
another KCF is used to learn the target area to estimate a new scale
of the target. However, because of running more than a KCF on each
frame, this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. Figure \ref{Workflows}
illustrates the work-flow of the {\it E}nKCF. In particular, to
maximize run-time performance and accuracy, instead of running them
all together on every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing a scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance.

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%----------------------------------------------------------------------

In this paper, we propose a novel way of utilizing a multiple of the
KCFs \cite{henriques2015high} to effectively handle scale variations
and dynamic maneuvers of a target. To maintain or improve the run-time
performance of the original KCF (e.g., $\ge$ 300), we deploy three
KCFs in turn, instead of applying them on the same image frame
together. Each of these KCFs is designed to address specific
challenges, i.e., scale and translation. By alternating their
deployments, our algorithm will improve the performance of the
original KCF while preserving the efficient nature and small-footprint
of the KCF computation.

@@

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!b]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}
\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

\textbf{{\it E}nKCF with Hand-crafted Features}
We, first, explore traditional features to run  {\it E}nKCF on any embedded system as it is the primary
objective of this study. In this direction, we employ two highly efficient features; fHoG \cite{felzenszwalb2010object}
and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$ assigned hand-crafted features, . This version of {\it E}nKCF is dedicated to run
on any embedded system at real-time ($30$fps).

\textbf{{\it E}nKCF with Convolutional Neural Network Features}
In addition to hand-crafted featurres, we explore deep features
to boost tracking performance. This version of {\it E}nKCF, on the other hand, 
is dedicated to run on high-end embedded systems (GPUs).

There have been many studies on applying a pretrained CNN features to
tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet
\cite{simonyan2014very} for this idea where their experiments showed
that the first convolutional layer features lead to slightly better
precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
features. Their method employs the third convolutional layer features
to get the response map. In the next stage, they used the estimation
of the target's transition from the first stage to use the second
convolutional layer features. Finally, the first convolutional layer
features is extracted from the position estimated in the second
stage. This coarse-to-fine position estimation approach allows to
utilize more representative features of the object. However, such
approach requires multiple runs of a KCF at a single frame, increasing
the run-time complexity. For this reason, we follow a similar approach
to \cite{danelljan2015convolutional} to embed deep learning features.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed  {\it
  E}nKCF with hand-crafted features, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 data is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 data, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, we call it
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

\textbf{Features Selections} We used different features for each of
three KCFs as each of them has different goals to accomplish. In
particular, the translation filter, $R_{t}^{L}$, uses both the fast
Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to more effectively
learn the background around the target as shown in figure~\ref{fig:Filters}. 
Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
translation filter, $R_{t}^{S}$, worked well when it used fHoG
features only; the scale filter, $R_{s}$ did when it used both fHoG
and color features.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. We hypothesize that the {\it E}nKCF
tracker could perform better with deep features trained on ImageNet
dataset. Utilizing pretrained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. But as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ conv features as shown in figure~\ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

  Burak: We don't expect the reviewers or readers to exactly see what
  we saw here. Keep their scales same -- whatever maximum value you
  choose for the y-axis for one graph, use the same scale to all other
  same graphs.}
\end{comment}

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC).
